Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-03-26 paper.qmd
correct error detecteds in improved figure

   subgraph cluster_2 {
     graph[shape = rectangle]
         C2b [label = 'Exploration']
         C2a [label = 'CRUSE\ncounty level results']
         C2 [label = 'CRUSE\nnational map']
         B2 [label = 'CRUSE\nlanding page']
         A2 [label = 'Non professional\nuser'] 
}

@@

  # node (triangle)
  #################
  node [shape = diamond]
         Dd1 [label = 'External\ntools']
         C2b1 [label = 'Communication']
  # edges 
  #######
  A2 -> B2
  A -> B
  B -> C
  B2 -> C2
  C -> D
  C2 -> C2a
  C2 -> C2b
  C2b -> C2b1
  D -> Da 
  D -> Db 
  D -> Dc 
  D -> Dd 
  Dd -> Dd1

>>>>

   subgraph cluster_2 {
     graph[shape = rectangle]
         C2b [label = 'Exploration']
         C2a [label = 'CRUSE\ncounty level results']
         C2 [label = 'CRUSE\nnational map']
         B2 [label = 'CRUSE\nlanding page']
         A2 [label = 'Non-professional\nuser'] 
}

@@

  # node (triangle)
  #################
  node [shape = diamond]
         Dd1 [label = 'External\ntools']
         C2b1 [label = 'Communication']
  # edges 
  #######
  A2 -> B2
  A -> B
  B -> C
  B2 -> C2
  C -> D
  C2 -> C2a
  C2 -> C2b
  C2a -> C2b
  C2b -> C2b1
  D -> Da 
  D -> Db 
  D -> Dc 
  D -> Dd 
  Dd -> Dd1
